Hydrodynamics of a Semipermeable Vesicle Under Flow and Confinement

### 2021-01-20 vesicle_code/docs/permeableVes/main.tex
small fixes

% Please include corresponding author, author contribution and author declaration information
\authorcontributions{B. Q. and Y.-N. Y. designed research with A. G.'s assistance. B.Q. and Y.-N.Y.
performed the research, analyzed the data, and wrote the paper.}
%\authordeclaration{Please declare any competing interests here.}
\correspondingauthor{\textsuperscript{1} E-mail: yyoung@njit.edu}

% At least three keywords are required at submission. Please provide three to five keywords, separated by the pipe symbol.
\keywords{Semipermeable membrane$|$ Vesicle $|$ Extreme confinement $|$
Boundary Integral Equations $|$ Stokes flow}

\begin{abstract}
Lipid bilayer membranes have a native (albeit small) permeability for
water molecules. Under an external load, 
provided that the bilayer structure stays intact and does
not suffer from poration or rupture,
a lipid membrane deforms and
its water influx/efflux is often assumed negligible in the absence of
osmolarity. 
%
In this work we use boundary integral simulations to investigate the
effects of native water permeability on the vesicle hydrodynamics due to
a mechanical load,  such as the viscous stress from an external flow
deforming a vesicle membrane in free space or pushing it through a
confinement. Coupling the membrane permeability with membrane elastic
stress and tension in the framework of Helfrich free energy, we
illustrate that, in the absence of an osmotic stress gradient, the
model semipermeable vesicle is affected by water influx/efflux over a
sufficiently long time or under a strong confinement. Our simulation
results quantify the conditions for water permeation to be negligible
in terms of the time scales, flow strength, and confinement. These
results shed light on how microfluidic confinement can be utilized to
estimate membrane permeability.
%
%Lipid bilayer membranes have a native (albeit small) permeability for
%water molecules. Under load, as long as the bilayer membrane stays intact (no poration or rupture), the water influx/efflux is
%often assumed negligible in the absence of a osmolarity pressure across the membrane. 
%%
%In this work we focus on physical regimes where the membrane tension is below the critical value for membrane poration, and use boundary integral simulations to
%investigate the effects of native water permeability on the hydrodynamics of
%a vesicle under various flows and confinement configurations. 
%%
%Coupling the membrane permeability with membrane elastic stress, tension, and
%mechanical stress in the framework of Helfrich free energy, we
%illustrate that, in the absence of an osmotic stress gradient, a giant
%unilamellar vesicle may be significantly affected by water
%influx/efflux over a sufficiently long time or under a strong
%confinement. Our simulation results quantify the conditions for water
%permeation to be negligible in terms of the time scales, flow strength
%of an external flow, and degree of confinement. These results shed
%light on how microfluidic confinement can be utilized to estimate
%membrane permeability.
%%
%%osmotic stress gradient 
%%We describe a mathematical model for a semipermeable vesicle and derive
%%  a boundary integral equation formulation for simulating its
%%  hydrodynamics.  
%%
%%Please provide an abstract of no more than 250 words in a single paragraph. Abstracts should explain to the general reader the major contributions of the article. References in the abstract must be cited in full within the abstract itself and cited in the text.
\end{abstract}

@@

questions, we investigate the balance between hydrodynamics stresses, tension,
and elastic stress of a semipermeable membrane under various flowing
conditions and confinement, see Figure~\ref{fig:sketch}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Formulation}
\begin{figure*}[hbp]
  \centering
  \ifTikz
  \input{figures/relaxationComposite.tikz}
  \else
  \includegraphics{figures/relaxationComposite.pdf}
  \fi
  \caption{\label{fig:relaxationComposite} (a) Snapshots of four
  semipermeable vesicles with $\beta = 10^{-7}$ submerged in a fluid
  with no background flow flow. Time goes from left to right. The red
  regions correspond to influx and the blue regions correspond to
  efflux. In all cases, the vesicle reaches a steady state circular
  shape. (b) The reduced area of each of the simulations. The particular
  snapshots in (a) occur at the marks along the curve.}
\end{figure*}
We consider a two-dimensional semipermeable vesicle (permeable only to
water) suspended in a viscous fluid (Figure~\ref{fig:sketch}), and we
let $\gamma$ denote the membrane boundary. We let
$\alpha=4\pi A/L^2$ be the vesicle's reduced area where $A$ is its area
and $L$ is its length. To focus on the effect of water flow on vesicle
hydrodynamics in various conditions, we assume the fluid is the same
inside and outside the vesicle membrane. On the membrane the permeable
water flux gives rise to a difference between the fluid velocity
${\uu}({\xx}\in \gamma)$ and the membrane velocity
$\dot{\xx}$~\cite{yao-mor2017}:
\begin{align}
  \uu - \dot{\xx} = - k_w (R T \triangle c + \ff_\mathrm{mem} \cdot \nn) \nn, \qquad
  \xx \in \gamma,
\end{align}
where $\nn$ is the outward normal (Figure~\ref{fig:sketch}), $k_w$ is
the hydraulic permeability, $R$ is the ideal gas constant, $T$ is the
temperature ($^{\circ}$K), $\triangle c$ is contrast in a solute
concentration (mol/volume), and $\ff_\mathrm{mem}$ is the membrane
stress that consists of both bending $ \ff_\mathrm{ben}= -k_b
\xx_{ssss}$ and tension $\ff_\mathrm{ten}=(\sigma \xx_s)_s$ ($s$ is the
arclength and $\sigma$ is the membrane tension along the membrane, see Supplementary Material). Using
$k_w\sim 10^{-12}$ m$^2$s/kg (typical of mammalian cell
membranes~\cite{LiMoriSun2015_PRL}) and an osmolarity $\triangle c =
0.1$ mol/L (consistent with the osmotic forces in vesicle aspiration
experiments~\cite{OlbrichRawiczNeedhamEtAl2000_BJ}), the corresponding
water flow is of the order $v_\mathrm{o}=0.1 \mu$m/s. Assuming that the
membrane bending stiffness $k_b = 10^{-19}$J, a membrane tension
$10^{-3}$N/m (one tenth of the lysis tension), and a characteristic
length scale of $10^{-6}$m, the tension contribution ($v_\mathrm{t}$)
and elastic stress contribution ($v_\mathrm{e}$) to the permeable water
flow can be scaled to $v_\mathrm{o}$ as
$v_\mathrm{o}:v_\mathrm{t}:v_\mathrm{e}=10^{0}:10^{-2}:10^{-6}$.
Furthermore, we note that in the absence of an osmotic stress, the water
permeable flow can be significant when the membrane tension is large due
to the external stress such as the hydrodynamic stress due to an
external flow or confinement. In the following we explore both.

@@

In experiments, vesicles under shear flows are measured for a minute
(chapter 19 in~\cite{Dimova2020_GVB}), a duration over which vesicle can
be assumed impermeable~\cite{AbkarianViallat2005_BJ}. Our simulations of
a semipermeable vesicle in these flows show that water permeability may
lead to different vesicle hydrodynamics over a time scale of 10 to 100
minutes. For vesicles in a narrow microfluidic channel, the experiments
usually do not last longer than a few minutes~\cite{abk-fai-sto2006}.
Our simulations show that strong confinement can lead to amplification
of water permeability at such short time scales.

@@

In Figure~\ref{fig:relaxationComposite}, we examine the relaxation
dynamics of a semipermeable vesicle with four initial shapes and reduced
areas as labeled. The vesicles on the left are color-coded by the water
permeation flux: red denotes an influx into the vesicle, and blue
denotes an efflux out of the vesicle.
%
First we observe that the initial vesicle shape determines the direction
of water flux. For the vesicle with an initial reduced area
($\alpha(0)=0.12$ in the bottom row) the vesicle deflates (blue regions)
first due to the high interior capillary pressure that corresponds to
the high membrane curvatures. For the other three cases efflux is found
at some locations of high curvature, while mostly water permeates into
the vesicle and significant change in the reduced area is found at
$t\sim 1$ hour. Over time (about ten days) all vesicles inflate and as
expected, each vesicle eventually reaches a circular shape with reduced
area $\alpha=1$. 
%%These regions are denoted in blue and are only present at early times. 
%Finally, the vesicles's reduced area do not steady state tension is
%$\Lambda = 2\pi^2/L^2$. 
%Therefore, the times for the vesicle to deviate from its initial reduced area and to reach its
%steady state are proportional to $\beta^{-1}$. 
%
%Each of the four cases in Figure~\ref{fig:relaxationComposite} eventually
%reaches a circular shape with reduced area $\alpha=1$. Next, we observe
%that even though the vesicle is inflating to a circle, 
%%meaning that there is a net flux into the vesicle, 
%there are regions where the flux
%is out of the vesicle. These regions are denoted in blue and are only
%present at early times. 
%
%Finally, the vesicles's reduced area do not
%change by much at early times (up to ten minutes), and

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Semipermeable Vesicle in a Narrow Channel (Stenosis)}
 \begin{figure*}[hbp]
  \centering
  \ifTikz
  \input{figures/stenosisComposite.tikz}
  \else
  \includegraphics{figures/stenosisComposite.pdf}
  \fi
  \caption{\label{fig:stenosisComposite} (a) A semipermeable vesicle
   passing through a closely-fit channel similar to the experimental
   device in~\cite{abk-fai-sto2006}. (b) A semipermeable vesicle passing
   through a  (four-times) longer closely-fit channel than (a). (c) The
   excess pressure of an impermeable and semipermeable vesicle in the
   short geometry in (a). (d) The reduced area of the semipermeable
   vesicles in the geometries in (a) and (b) as a function of the
   vesicles' center of mass. In (c) and (d), the $x$-axis is scaled by
   $1/L$ where $L$ is half the length of the constriction. (e) The
   reduced area of the semipermeable vesicles in the geometries in (a)
   and (b) as a function of time. The time axis is scaled by $1/t_R$
   where $t_R$ is the residency time. In parts (c) and (d), the dashed
   lines correspond to the locations of the inlet and outlet. In part
   (e), the dashed lines correspond to the times that the vesicle enters
   and exits the constriction. The colored vesicles show the tension
   distribution in N/m of the circled vesicles. Throughout the entire
   simulation, these vesicle configurations have the largest tension.}
\end{figure*}

Cells experience stretching and release messengers when they pass
through capillary vessels~\cite{Wan2008_PNAS, ForsythWan2011_PNAS,
Pak2015_PNAS}. Many cells exhibit extraordinary flexibility as they go
through narrow channels~\cite{AuStoreyMoore2016_PNAS}, and adjustment of
area to volume ratio may be a key factor for a successful passage.  Here
we quantify the effect of water permeability on a vesicle going through
a stenosis (a long microfluidic channel with a width smaller than the
cell radius).  Based on the findings in~\cite{abk-fai-sto2006}, we first
examine the effect of semipermeability on the pressure fluctuation
across a stenosed geometry. In this experiment, a pressure drop is used
to squeeze a red blood cell through a constriction with diameter $5\mu$m
and length $45\mu$m. We set up a similar computational geometry with a
Poiseuille flow imposed at the inlet and outlet
(Figure~\ref{fig:stenosisComposite}(a)). The flow velocity $U_{max} =
1000 \;\mu$m/s is maintained at the inlet and outlet and is chosen so that
the residency time of the vesicle in the stenosis channel is $t_R
\approx 25$ ms which agrees with the experimental
results~\cite{abk-fai-sto2006}. When the red blood cell enters the
channel, an increase in the pressure drop is required to maintain a
constant flow rate, and the difference in the pressure drop is called
the excess pressure.

@@

Figures~\ref{fig:stenosisComposite}(d)
and~\ref{fig:stenosisComposite}(e) show that the vesicle deflates from
the beginning due to the high flow velocity, consistent with the results
for a vesicle in a Poiseuille flow in open space (blue curves). As the
vesicle enters the stenosis channel, it continues to deflate in the
front even though we observe influx (red segment) at various rear
locations in the membrane. Overall, the vesicle loses about 6.1\% of its
initial total water at a constant rate as shown in
Figures~\ref{fig:stenosisComposite}(d)
and~\ref{fig:stenosisComposite}(e). Thus we expect that a larger amount
of deflation is possible if the vesicle is inside a longer stenosis: we
consider a vesicle passing through a channel of triple the length in
Figure~\ref{fig:stenosisComposite}(b) with $U_{\max}=1000\;\mu$m/s, and we
observe that vesicle stays inside the stenosis for a residence time $t_R
\approx 70$ ms and the reduced area decreases by 13.2\% (red curves).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Semipermeable Vesicle in a Contracting Geometry} 
\begin{figure}[htp]
  \centering
  \ifTikz
  \input{figures/contractingComposite.tikz}
  \else
  \includegraphics{figures/contractingComposite.pdf}
  \fi
  \caption{\label{fig:contractingComposite} A contracting channel
  similar to the experimental configuration in~\cite{wu2015critical}. The
  channel width varies from $18\;\mu$m to $1.8\;\mu$m, and it repeats every
  $45\;\mu$m. The fluid flux along the red regions is into the vesicle,
  and the fluid flux along the blue regions is out of the vesicle.
  (a--c): The ability for a semipermeable vesicle to pass through the
  contraction depends on the semipermeability rate. (d--f): The ability
  for a semipermeable vesicle to pass through the contraction depends
  on the flow rate. The colored vesicles show the tension distribution
  in N/m of the circled vesicles. Throughout the entire simulation,
  these vesicle configurations have the largest tension.}
\end{figure}

Squeezing a cell or an elastic vesicle through a slit in microfluidics
has gained popularity for its application in stress-induced release of
macromolecules~\cite{ShareiEtAl2013_PNAS, Pak2015_PNAS,
ZhangShenHoganBarakatMisbah2018_BJ, LuoBai2019_PoF}. Red blood cells go
through submicron slits many times during their lifetime, and such
process selects healthy, flexible red blood cells to
survive~\cite{wu2015critical,LuPeng2019_PoF}. Here we investigate the
role of membrane permeability to water when a semipermeable vesicle is
squeezed through a contracting microfluidic channel similar
to~\cite{wu2015critical}, where the width of the channel gradually
decreases from $18 \;\mu$m to $1.8\; \mu$m. The channel then immediately
reopens to $18 \mu$m (Figure~\ref{fig:contractingComposite}). A
Poiseuille flow is imposed at the inlet and outlet with a constant
maximum flow rate of $U_{\max}$. We initialize a semipermeable vesicle
with $\alpha = 0.65$ that spans $10\; \mu$m of the total channel width and
investigate the effects of the membrane permeability to water and the
maximum flow velocity on whether a vesicle can successfully pass through
the slit. We color the vesicle according to the sign of its flux---red
for influx and blue for efflux.

In Figures~\ref{fig:contractingComposite}(a)
and~\ref{fig:contractingComposite}(b), we plot snapshots of vesicles
with different permeability $\beta$.
Figure~\ref{fig:contractingComposite}(c) shows the corresponding reduced
area as a function of the vesicle's location. We observe that if the
permeability is sufficiently large, the vesicle inflates gradually over
seconds before it reaches the neck, and then it quickly deflates within
a fraction of a second. However, if the semipermeability rate is too
low, the vesicle is too large when it reaches the narrowest part of the
channel, and it is unable to pass. In
Figures~\ref{fig:contractingComposite}(d)
and~\ref{fig:contractingComposite}(e), we plot snapshots of vesicles
with different imposed maximum velocities, and
Figure~\ref{fig:contractingComposite}(f) shows the reduced area as a
function of the vesicle's location. At low velocities, the vesicle
inflates similar to the unbounded parabolic flow example, and it is
unable to pass through the contraction. However, higher flow rates
result in additional deflation and the vesicle passes through the
contraction.
\begin{figure}[htp]
  \centering
  \ifTikz
  \input{figures/contractingComposite2.tikz}
  \else
  \includegraphics{figures/contractingComposite2.pdf}
  \fi
  \caption{\label{fig:contractingComposite2} Vesicle reduced area and
  velocity vs.~time. Permeability rate is $\beta = 10^{-3}$ and maximum
  velocity is $18\mu$m/s. (a) A semipermeable vesicle passing through
  six periods of the contracting geometry. (b) The reduced area with
  the marks representing shapes in (a). (c) The vesicle velocity with
  the marks representing shapes in (a). In (b) and (c), the bottom
  x-axis is the $x$-coordinate of the center of mass, and the upper
  x-axis is time. The colored vesicles show the tension distribution in
  N/m of the circled vesicles. Throughout the entire simulation, these
  vesicle configurations have the largest tension.}
\end{figure}

@@

\section*{Discussion}
In this work we investigated the effects of membrane permeability to
water on vesicle hydrodynamics. Without any external flow or
confinement, our analysis shows that a semipermeable vesicle always
inflates to maximize the water content inside the vesicle of a fixed
length (area) in two (three) dimensions. Results from analysis and
numerical simulation show that such relaxation of a semipermeable
vesicle is characterized by a rescaled time $\beta t$. We further
illustrate that the relaxation process consists of at least two phases:
The first phase is dominated by the balance between membrane traction
and viscous stress at early times (up to five minutes), when the vesicle
behaves like an impermeable membrane. The second phase sets in after a
few hours, when water influx begins to dominate and inflate the
vesicle. Over a time scale of more than ten days, a semipermeable vesicle is
fully inflated, independent of its initial surface-to-volume ratio.
%\todo[inline]{Do the time scales in this paragraph reflect the
%adjustments we made to $\beta$ for the quiescent case?}

@@

\acknow{We thank Howard Stone for suggestions .
B.Q.~acknowledges support from the Simons Foundation, Mathematics and
Physical Sciences-Collaboration Grants for Mathematicians, Award Number
527139. Y.-N.Y.~acknowledges support from NSF (DMS 1614863, DMS 195160) and Flatiron Institute, part of Simons Foundation.}

>>>>

% Please include corresponding author, author contribution and author declaration information
\authorcontributions{B.Q.~and Y.-N.Y.~designed and perfored research
with A.~G.'s assistance. B.Q.~and Y.-N.Y.~analyzed the data and wrote
the paper.}
%\authordeclaration{Please declare any competing interests here.}
\correspondingauthor{\textsuperscript{1} E-mail: yyoung@njit.edu}

% At least three keywords are required at submission. Please provide three to five keywords, separated by the pipe symbol.
\keywords{Semipermeable membrane$|$ Vesicle $|$ Extreme confinement $|$
Boundary integral equations $|$ Stokes flow}

\begin{abstract}
Lipid bilayer membranes have a native (albeit small) permeability for
water molecules. Under an external load, 
provided that the bilayer structure stays intact and does
not suffer from poration or rupture,
a lipid membrane deforms and
its water influx/efflux is often assumed negligible in the absence of
osmolarity. 
%
In this work we use boundary integral simulations to investigate the
effects of native water permeability on the vesicle hydrodynamics due to
a mechanical load,  such as the viscous stress from an external flow
deforming a vesicle membrane in free space or pushing it through a
confinement. Coupling the membrane permeability with membrane elastic
stress and tension in the framework of Helfrich free energy, we
illustrate that, in the absence of an osmotic stress gradient, the
semipermeable vesicle is affected by water influx/efflux over a
sufficiently long time or under a strong confinement. Our simulation
results quantify the conditions for water permeation to be negligible
in terms of the time scales, flow strength, and confinement. These
results shed light on how microfluidic confinement can be utilized to
estimate membrane permeability.
%
%Lipid bilayer membranes have a native (albeit small) permeability for
%water molecules. Under load, as long as the bilayer membrane stays intact (no poration or rupture), the water influx/efflux is
%often assumed negligible in the absence of a osmolarity pressure across the membrane. 
%%
%In this work we focus on physical regimes where the membrane tension is below the critical value for membrane poration, and use boundary integral simulations to
%investigate the effects of native water permeability on the hydrodynamics of
%a vesicle under various flows and confinement configurations. 
%%
%Coupling the membrane permeability with membrane elastic stress, tension, and
%mechanical stress in the framework of Helfrich free energy, we
%illustrate that, in the absence of an osmotic stress gradient, a giant
%unilamellar vesicle may be significantly affected by water
%influx/efflux over a sufficiently long time or under a strong
%confinement. Our simulation results quantify the conditions for water
%permeation to be negligible in terms of the time scales, flow strength
%of an external flow, and degree of confinement. These results shed
%light on how microfluidic confinement can be utilized to estimate
%membrane permeability.
%%
%%osmotic stress gradient 
%%We describe a mathematical model for a semipermeable vesicle and derive
%%  a boundary integral equation formulation for simulating its
%%  hydrodynamics.  
%%
%%Please provide an abstract of no more than 250 words in a single paragraph. Abstracts should explain to the general reader the major contributions of the article. References in the abstract must be cited in full within the abstract itself and cited in the text.
\end{abstract}

@@

questions, we investigate the balance between hydrodynamics stresses,
tension, and elastic stress of a semipermeable membrane under various
flowing conditions and confinement (see Figure~\ref{fig:sketch}).

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Formulation}
\begin{figure*}[hbp]
  \centering
  \ifTikz
  \input{figures/relaxationComposite.tikz}
  \else
  \includegraphics{figures/relaxationComposite.pdf}
  \fi
  \caption{\label{fig:relaxationComposite} (a) Snapshots of four
  semipermeable vesicles with $\beta = 10^{-7}$ submerged in a fluid
  with no background flow flow. Time goes from left to right. The red
  regions correspond to influx and the blue regions correspond to
  efflux. In all cases, the vesicle reaches a steady state circular
  shape. (b) The reduced area of each of the simulations. The particular
  snapshots in (a) occur at the marks along the curve.}
\end{figure*}
We consider a two-dimensional semipermeable vesicle (permeable only to
water) suspended in a viscous fluid (Figure~\ref{fig:sketch}), and we
let $\gamma$ denote the membrane boundary. We let
$\alpha=4\pi A/L^2$ be the vesicle's reduced area where $A$ is its area
and $L$ is its length. To focus on the effect of water flow on vesicle
hydrodynamics in various conditions, we assume the fluid is the same
inside and outside the vesicle membrane. On the membrane the permeable
water flux gives rise to a difference between the fluid velocity
${\uu}({\xx}\in \gamma)$ and the membrane velocity
$\dot{\xx}$~\cite{yao-mor2017}:
\begin{align}
  \uu - \dot{\xx} = - k_w (R T \triangle c + \ff_\mathrm{mem} \cdot \nn) \nn, \qquad
  \xx \in \gamma,
\end{align}
where $\nn$ is the outward normal (Figure~\ref{fig:sketch}), $k_w$ is
the hydraulic permeability, $R$ is the ideal gas constant, $T$ is the
temperature (K), $\triangle c$ is contrast in a solute concentration
(mol/volume), and $\ff_\mathrm{mem}$ is the membrane stress that
consists of both bending $ \ff_\mathrm{ben}= -k_b \xx_{ssss}$ and
tension $\ff_\mathrm{ten}=(\sigma \xx_s)_s$ ($s$ is the arclength and
$\sigma$ is the membrane tension along the membrane, see Supplementary
Material). Using $k_w\sim 10^{-12}$ m$^2$s/kg (typical of mammalian cell
membranes~\cite{LiMoriSun2015_PRL}) and an osmolarity $\triangle c =
0.1$ mol/L (consistent with the osmotic forces in vesicle aspiration
experiments~\cite{OlbrichRawiczNeedhamEtAl2000_BJ}), the corresponding
water flow is of the order $v_\mathrm{o}=0.1 \; \mu$m/s. Assuming a
membrane bending stiffness of $k_b = 10^{-19}$ J, a membrane tension of
$10^{-3}$ N/m (one tenth of the lysis tension), and a characteristic
length scale of $10^{-6}$ m, the tension contribution ($v_\mathrm{t}$)
and elastic stress contribution ($v_\mathrm{e}$) to the permeable water
flow can be scaled to $v_\mathrm{o}$ as
$v_\mathrm{o}:v_\mathrm{t}:v_\mathrm{e}=10^{0}:10^{-2}:10^{-6}$.
Furthermore, we note that in the absence of an osmotic stress, the water
permeable flow can be significant when the membrane tension is large due
to the external stress such as the hydrodynamic stress due to an
external flow or confinement. In the following we explore both.

@@

In experiments, vesicles under shear flows are measured for a minute
(chapter 19 in~\cite{Dimova2020_GVB}), a duration over which a vesicle
can be assumed impermeable~\cite{AbkarianViallat2005_BJ}. Our
simulations of a semipermeable vesicle in these flows show that water
permeability may lead to different vesicle hydrodynamics over a time
scale of 10 to 100 minutes. For vesicles in a narrow microfluidic
channel, the experiments usually do not last longer than a few
minutes~\cite{abk-fai-sto2006}. Our simulations show that strong
confinement can lead to amplification of water permeability at such
short time scales.

@@

In Figure~\ref{fig:relaxationComposite}, we examine the relaxation
dynamics of a semipermeable vesicle with four initial shapes and reduced
areas as labeled. The vesicles on the left are color-coded by the water
permeation flux: red denotes an influx into the vesicle, and blue
denotes an efflux out of the vesicle. First we observe that the initial
vesicle shape determines the direction of water flux. For the vesicle
with an initial reduced area $\alpha(0)=0.12$ (bottom row) the vesicle
deflates (blue regions) first due to the high interior capillary
pressure that corresponds to the high membrane curvatures. For the other
three cases efflux is found at some locations of high curvature, while
mostly water permeates into the vesicle and significant change in the
reduced area is found at $t\sim 1$ hour. Over time (about ten days) all
vesicles inflate and as expected, each vesicle eventually reaches a
circular shape with reduced area $\alpha=1$. 
%%These regions are denoted in blue and are only present at early times. 
%Finally, the vesicles's reduced area do not steady state tension is
%$\Lambda = 2\pi^2/L^2$. 
%Therefore, the times for the vesicle to deviate from its initial reduced area and to reach its
%steady state are proportional to $\beta^{-1}$. 
%
%Each of the four cases in Figure~\ref{fig:relaxationComposite} eventually
%reaches a circular shape with reduced area $\alpha=1$. Next, we observe
%that even though the vesicle is inflating to a circle, 
%%meaning that there is a net flux into the vesicle, 
%there are regions where the flux
%is out of the vesicle. These regions are denoted in blue and are only
%present at early times. 
%
%Finally, the vesicles's reduced area do not
%change by much at early times (up to ten minutes), and

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Semipermeable Vesicle in a Narrow Channel (Stenosis)}
 \begin{figure*}[htp]
  \centering
  \ifTikz
  \input{figures/stenosisComposite.tikz}
  \else
  \includegraphics{figures/stenosisComposite.pdf}
  \fi
  \caption{\label{fig:stenosisComposite} (a) A semipermeable vesicle
   passing through a closely-fit channel similar to the experimental
   device in~\cite{abk-fai-sto2006}. (b) A semipermeable vesicle passing
   through a  (four-times) longer closely-fit channel than (a). (c) The
   excess pressure of an impermeable and semipermeable vesicle in the
   short geometry in (a). (d) The reduced area of the semipermeable
   vesicles in the geometries in (a) and (b) as a function of the
   vesicles' center of mass. In (c) and (d), the $x$-axis is scaled by
   $1/L$ where $L$ is half the length of the constriction. (e) The
   reduced area of the semipermeable vesicles in the geometries in (a)
   and (b) as a function of time. The time axis is scaled by $1/t_R$
   where $t_R$ is the residency time. In parts (c) and (d), the dashed
   lines correspond to the locations of the inlet and outlet. In part
   (e), the dashed lines correspond to the times that the vesicle enters
   and exits the constriction. The colored vesicles show the tension
   distribution in N/m of the circled vesicles. Throughout the entire
   simulation, these vesicle configurations have the largest tension.}
\end{figure*}

\begin{figure}[hbp]
  \centering
  \ifTikz
  \input{figures/contractingComposite.tikz}
  \else
  \includegraphics{figures/contractingComposite.pdf}
  \fi
  \caption{\label{fig:contractingComposite} A contracting channel
  similar to the experimental configuration in~\cite{wu2015critical}.
  The channel width varies from $18\;\mu$m to $1.8\;\mu$m, and it
  repeats every $45\;\mu$m. The fluid flux along the red regions is into
  the vesicle, and the fluid flux along the blue regions is out of the
  vesicle.  (a--c): The ability for a semipermeable vesicle to pass
  through the contraction depends on the semipermeability rate. (d--f):
  The ability for a semipermeable vesicle to pass through the
  contraction depends on the flow rate. The colored vesicles show the
  tension distribution in N/m of the circled vesicles. Throughout the
  entire simulation, these vesicle configurations have the largest
  tension.}
\end{figure}

Cells experience stretching and release messengers when they pass
through capillary vessels~\cite{Wan2008_PNAS, ForsythWan2011_PNAS,
Pak2015_PNAS}. Many cells exhibit extraordinary flexibility as they go
through narrow channels~\cite{AuStoreyMoore2016_PNAS}, and adjustment of
area to volume ratio may be a key factor for a successful passage.  Here
we quantify the effect of water permeability on a vesicle going through
a stenosis (a long microfluidic channel with a width smaller than the
cell radius).  Based on the findings in~\cite{abk-fai-sto2006}, we first
examine the effect of semipermeability on the pressure fluctuation
across a stenosed geometry. In this experiment, a pressure drop is used
to squeeze a red blood cell through a constriction with diameter
$5\;\mu$m and length $45\;\mu$m. We set up a similar computational
geometry with a Poiseuille flow imposed at the inlet and outlet
(Figure~\ref{fig:stenosisComposite}(a)). The flow velocity $U_{\max} =
1000 \;\mu$m/s is maintained at the inlet and outlet and is chosen so
that the residency time of the vesicle in the stenosis channel is $t_R
\approx 25$ ms which agrees with the experimental
results~\cite{abk-fai-sto2006}. When the red blood cell enters the
channel, an increase in the pressure drop is required to maintain a
constant flow rate, and the difference in the pressure drop is called
the excess pressure.

@@

Figures~\ref{fig:stenosisComposite}(d)
and~\ref{fig:stenosisComposite}(e) show that the vesicle deflates from
the beginning due to the high flow velocity, consistent with the results
for a vesicle in a Poiseuille flow in open space (blue curves). As the
vesicle enters the stenosis channel, it continues to deflate in the
front even though we observe influx (red segment) at various rear
locations in the membrane. Overall, the vesicle loses about 6.1\% of its
initial total water at a constant rate as shown in
Figures~\ref{fig:stenosisComposite}(d)
and~\ref{fig:stenosisComposite}(e) (blue curves). Thus we expect that a
larger amount of deflation is possible if the vesicle is inside a longer
stenosis: we consider a vesicle passing through a channel of triple the
length in Figure~\ref{fig:stenosisComposite}(b) with
$U_{\max}=1000\;\mu$m/s, and we observe that vesicle stays inside the
stenosis for a residence time $t_R \approx 70$ ms and the reduced area
decreases by 13.2\% (red curves).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Semipermeable Vesicle in a Contracting Geometry} 
Squeezing a cell or an elastic vesicle through a slit in microfluidics
has gained popularity for its application in stress-induced release of
macromolecules~\cite{ShareiEtAl2013_PNAS, Pak2015_PNAS,
ZhangShenHoganBarakatMisbah2018_BJ, LuoBai2019_PoF}. Red blood cells go
through submicron slits many times during their lifetime, and such
process selects healthy, flexible red blood cells to
survive~\cite{wu2015critical,LuPeng2019_PoF}. Here we investigate the
role of membrane permeability to water when a semipermeable vesicle is
squeezed through a contracting microfluidic channel similar
to~\cite{wu2015critical}, where the width of the channel gradually
decreases from $18 \;\mu$m to $1.8\; \mu$m. The channel then immediately
reopens to $18\;\mu$m (Figure~\ref{fig:contractingComposite}). A
Poiseuille flow is imposed at the inlet and outlet with a constant
maximum flow rate of $U_{\max}$. We initialize a semipermeable vesicle
with $\alpha = 0.65$ that spans $10\; \mu$m of the total channel width and
investigate the effects of the membrane permeability to water and the
maximum flow velocity on whether a vesicle can successfully pass through
the slit. We color the vesicle according to the sign of its flux---red
for influx and blue for efflux.

In Figures~\ref{fig:contractingComposite}(a)
and~\ref{fig:contractingComposite}(b), we plot snapshots of vesicles
with different permeability $\beta$.
Figure~\ref{fig:contractingComposite}(c) shows the corresponding reduced
area as a function of the vesicle's location. We observe that if the
permeability is sufficiently large, the vesicle inflates gradually over
seconds before it reaches the neck, and then it quickly deflates within
a fraction of a second. However, if the semipermeability rate is too
low, the vesicle is too large when it reaches the narrowest part of the
channel, and it is unable to pass. In
Figures~\ref{fig:contractingComposite}(d)
and~\ref{fig:contractingComposite}(e), we plot snapshots of vesicles
with different imposed maximum velocities, and
Figure~\ref{fig:contractingComposite}(f) shows the reduced area as a
function of the vesicle's location. At low velocities, the vesicle
inflates similar to the unbounded parabolic flow example, and it is
unable to pass through the contraction. However, higher flow rates
result in additional deflation and the vesicle passes through the
contraction.

\begin{figure}[hbp]
  \centering
  \ifTikz
  \input{figures/contractingComposite2.tikz}
  \else
  \includegraphics{figures/contractingComposite2.pdf}
  \fi
  \caption{\label{fig:contractingComposite2} Vesicle reduced area and
  velocity vs.~time. Permeability rate is $\beta = 10^{-3}$ and maximum
  velocity is $18\;\mu$m/s. (a) A semipermeable vesicle passing through
  six periods of the contracting geometry. (b) The reduced area with
  the marks representing shapes in (a). (c) The vesicle velocity with
  the marks representing shapes in (a). In (b) and (c), the bottom
  x-axis is the $x$-coordinate of the center of mass, and the upper
  x-axis is time. The colored vesicles show the tension distribution in
  N/m of the circled vesicles. Throughout the entire simulation, these
  vesicle configurations have the largest tension.}
\end{figure}

@@

\section*{Discussion}
In this work we investigated the effects of membrane permeability to
water on vesicle hydrodynamics. Without any external flow or
confinement, our analysis shows that a semipermeable vesicle always
inflates to maximize the water content inside the vesicle of a fixed
length (area) in two (three) dimensions. Results from analysis and
numerical simulation show that such relaxation of a semipermeable
vesicle is characterized by a rescaled time $\beta t$. We further
illustrate that the relaxation process consists of at least two phases:
The first phase is dominated by the balance between membrane traction
and viscous stress at early times (up to five minutes), when the vesicle
behaves like an impermeable membrane. The second phase sets in after a
few hours, when water influx begins to dominate and inflate the vesicle.
Over a time scale of more than ten days, a semipermeable vesicle is
fully inflated, independent of its initial surface-to-volume ratio.

@@

\acknow{We thank Howard Stone for suggestions. B.Q.~acknowledges support
from the Simons Foundation, Mathematics and Physical
Sciences-Collaboration Grants for Mathematicians, Award Number 527139.
Y.-N.Y.~acknowledges support from NSF (DMS 1614863, DMS 195160) and
Flatiron Institute, part of Simons Foundation.}
